An Exploration of Analysis Methods on Predictive Models of Student Success

### 2024-02-04 paper/paper.tex
Update build and clean scripts, and fix hyperlink color in paper.tex

\usepackage{graphicx}
\usepackage{hyperref}
\graphicspath{ {../figures} }

@@

            \subsubsection{Database System}
                I chose to create a PostgreSQL relational database to organize the cleansing pipeline for this project \cite{postrgesql}.
                PostgreSQL is an open source, performant, and reliable relational database system. 
                The clear syntax of Structured Query Language (SQL) for scripting transformations 
                and database operations enabled me to wrangle millions of rows efficiently.

>>>>

\usepackage{graphicx}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=black,
    filecolor=black,
    citecolor=black,    
    urlcolor=black,
}
\graphicspath{ {../figures} }

@@

            \subsubsection{Database System}
                I chose to create a PostgreSQL relational database to organize the cleansing pipeline for this project \cite{postgresql}.
                PostgreSQL is an open source, performant, and reliable relational database system. 
                The clear syntax of Structured Query Language (SQL) for scripting transformations 
                and database operations enabled me to wrangle millions of rows efficiently.
